Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Bug

meta.merge.alphadiversity <- function(pseq, index = "shannon") {
    alphadiversity  <- microbiome::global(pseq, index = index)
    base::merge(meta(pseq), alphadiversity, by=0, all=TRUE) %>%
        dplyr::rename(Sample_ID = Row.names) %>%
            dplyr::mutate(BL_AGE_GROUP = group_age(dset.alpha$BL_AGE))
}
```

>>>>

meta.merge.alphadiversity <- function(pseq, index = "shannon") {
    alphadiversity  <- microbiome::global(pseq, index = index)
    base::merge(meta(pseq), alphadiversity, by=0, all=TRUE) %>%
        dplyr::rename(Sample_ID = Row.names) %>%
            dplyr::mutate(BL_AGE_GROUP = group_age(BL_AGE))
}
```
